\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-31 article/main.tex
modified:   article/main.tex

% Need result table

@@

\subsubsection{Language dependance}

@@

\subsubsection{Detection Level}

\begin{center}
\includegraphics[scale=0.75]{detection_level.png}
\end{center}

>>>>

\includegraphics[scale=0.75]{flux.png}

@@

\subsubsection{Language dependance}
The majority of techniques are language dependant and the most used 
languages are Java and C++

@@

But those detection methods can be easily converted to other languages
just by modifying the font-end.

\subsubsection{Detection Level}
We found out that almost all of design patterns detection methods 
identify the patterns on a source code level, though, the detection could
be done on multiple levels.
\begin{center}
\includegraphics[scale=0.75]{detection_level.png}
\end{center}
